---
title: "Project 2"
output: html_document
---

### Your assignment is to recreate this HTML document using R Markdown  

- Due Nov 15 at 5 p.m.
- Email your **.Rmd** file to lapatodm@mymail.vcu.edu and timothy.york@vcuhealth.org
- Format your file name exactly as: `lastname-hgen517-project2.Rmd`
- Include all text in your answer including these instructions


<br>

Load the `iris` data.frame that comes with base R.  
```{r, load.data, echo=T, eval=T}
data(iris)

```

<br>

### Create the following figures using `iris`  

<br>

#### Figure 1  
```{r, fig1, echo=F}
hist(iris$Sepal.Length, xlab= "Sepal Length", main= "Histogram of Sepal Length")
```

<br>

#### Figure 2  
```{r, fig2, echo=F}
plot(iris[,1:4], main= "Scatter Plots of Iris Data")
```

<br>

#### Figure 3  
```{r, fig3, echo=F}
plot(iris$Petal.Length, iris$Petal.Width, pch=20, col= iris$Species, main= NULL, xlab='Petal Length', ylab='Petal Width')
legend("topleft", c('setosa','versicolor','virginica'), pch= 20, col= c(1,2,3))
```

<br>

#### Figure 4  
```{r, fig4, echo=F}
plot(iris[iris$Species=='virginica','Petal.Length'], iris[iris$Species=='virginica','Petal.Width'], 
     pch=20, col= 'green', main= NULL, xlab='Petal Length', ylab='Petal Width')
legend("topleft", c('virginica'), pch= 20, col= c(3))
```


*END*


